Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-02 xrb2/paper.tex
add nicole
add new figure

@@

@@

>>>>

\author{Nicole Ford}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:500Hz_runs} Temperature properties of the 500~Hz simulations.}
	\tablehead{\colhead{run} & \colhead{$\delta T$ (K)} & \colhead{$T_\mathrm{hi}$ (K)} & \colhead{$T_\mathrm{star}$ (K)}} 
	\startdata
	{\tt flame\_wave\_500}      & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	{\tt flame\_wave\_500\_hot} & $1.2\times 10^9$ & $2\times 10^8$ & $2\times 10^8$ \\
	{\tt flame\_wave\_500\_3E8} & $1.1\times 10^9$ & $3\times 10^8$ & $3\times 10^8$ \\
	{\tt flame\_wave\_500\_4E8} & $10^9$ & $4\times 10^8$ & $4\times 10^8$ \\
	\enddata
	%
\end{deluxetable}

@@

\subsection{Effect of Temperature Structure}

\begin{figure}[t]
\centering
\plotone{compare_500Hz_abar}
\caption{\label{fig:compare_500Hz_abar} Comparison of $\bar{A}$ for 3 different 500~Hz models with different neutron star temperatures, $T_\star$, and resulting envelope
structures.  We see that the hottest model has a faster propagating flame.}
\end{figure}

Figure~\ref{fig:compare_500Hz_abar} shows 3 different 500 Hz simulations with different initial temperature structures.
